---
title: "p8105_hw5_jl6321.Rmd"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

## Problem 2

```{r}
homicide = read_csv("data/homicide-data.csv")
```

The raw data contains `r nrow(homicide)` rows and `r ncol(homicide)` columns, including variables `r colnames(homicide)`. 

Create a city_state variable and summarize within cities to obtain the total number of homicides and the number of unsolved homicides: 

```{r}
homicide = 
  homicide %>% 
  mutate(
      city_state = str_c(city, state, sep = ", "),
      if_solved = case_when(disposition == "Closed without arrest" ~ "unsolved", 
                           disposition == "Open/No arrest" ~ "unsolved", 
                           disposition == "Closed by arrest" ~ "solved"))

num_homicide = 
  homicide %>% 
  group_by(city_state) %>% 
  summarize(
    total_homicide = n(), 
    unsolved_homicide = sum(if_solved == "unsolved")) 
num_homicide
```

Use the prop.test function to estimate the proportion of homicides that are unsolved and pull the estimated proportion and confidence intervals from the resulting tidy dataframe: 

```{r}
baltimore = 
  num_homicide %>% 
  filter(city_state == "Baltimore, MD") 
baltimore_prop = 
  prop.test(baltimore$unsolved_homicide, baltimore$total_homicide) %>% 
  broom::tidy()
```



## Problem 3