---
title: "p8105_hw5_jl6321.Rmd"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

## Problem 2

```{r}
homicide = read_csv("data/homicide-data.csv")
```

The raw data contains `r nrow(homicide)` rows and `r ncol(homicide)` columns, including variables `r colnames(homicide)`. 

Create a city_state variable and summarize within cities to obtain the total number of homicides and the number of unsolved homicides: 

```{r}
homicide = 
  homicide %>% 
  mutate(
      city_state = str_c(city, state, sep = ", "),
      if_solved = case_when(disposition == "Closed without arrest" ~ "unsolved", 
                           disposition == "Open/No arrest" ~ "unsolved", 
                           disposition == "Closed by arrest" ~ "solved"))

num_homicide = 
  homicide %>% 
  group_by(city_state) %>% 
  summarize(
    total_homicide = n(), 
    unsolved_homicide = sum(if_solved == "unsolved")) 
num_homicide
```

Use the prop.test function to estimate the proportion of homicides that are unsolved and pull the estimated proportion and confidence intervals from the resulting tidy dataframe: 

```{r}
baltimore = 
  num_homicide %>% 
  filter(city_state == "Baltimore, MD") 

baltimore_prop = 
  prop.test(baltimore$unsolved_homicide, baltimore$total_homicide) %>% 
  broom::tidy()

bal_estimate = 
  list(
  "proportion_estimate" = baltimore_prop %>% pull(estimate), 
  "lower_CI_bound" = baltimore_prop %>% pull(conf.low), 
  "upper_CI_bound" = baltimore_prop %>% pull(conf.high)) %>% 
  bind_rows()
bal_estimate
```

Run prop.test for each of the cities in the dataset, and extract both the proportion of unsolved homicides and the confidence interval for each: 

```{r}
all_city = 
  num_homicide %>% 
  mutate(
    prop_test = purrr::map2(.x = unsolved_homicide, .y = total_homicide,  ~prop.test(x = .x, n = .y)), 
    tidied_test = purrr::map(.x = prop_test, ~broom::tidy(.x))) %>% 
  select(-prop_test) %>% 
  unnest(tidied_test) %>% 
  select(city_state, estimate, conf.low, conf.high) 
```

Create a plot that shows the estimates and CIs for each city: 

```{r}
all_city %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  labs(x = "City, State", y = "Estimated Proportion with 95% CI",title = "Unsolved Homicides") + 
  scale_x_discrete(guide = guide_axis(angle = 90)) 
```


## Problem 3